---
title: "The P Hydro model with sox optimization"
author: "Victor Flo"
date: "`r Sys.Date()`"
output:
  html_document: null
  word_document: default
  toc: yes
  pdf_document: default
toc_depth: 3
toc_float: yes
---
  
```{r include=FALSE}
library(tidyverse)
library(purrr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(scales)
library(ggpubr)
```

The SOX stomatal scheme (Eller et al. 2018) is obtimised as:
$$
F = A_j  (\frac{k_\mathrm{\psi_l}-k_\mathrm{\psi_{crit}}}{K_\mathrm{max}-k_\mathrm{\psi_{crit}}})
$$

Then, accounting for photosynthetic cost:
$$
F = A_j  (\frac{k_\mathrm{\psi_l}-k_\mathrm{\psi_{crit}}}{K_\mathrm{max}-k_\mathrm{\psi_{crit}}}) - \alpha J_\mathrm{max}
$$

```{r, echo = FALSE, include = FALSE, message = FALSE}
source("../stomatal_optimization_functions.R")
source('../hydraulic_functions.R')
source('../photosynthetic_functions.R')
library(tidyverse)
library(rpmodel)

calc_gs_test <- function (dpsi, psi_soil, par_plant, par_env, ...){
  K = scale_conductivity_ks(par_plant$conductivity, par_env, par_plant, do_backtransform = FALSE) #mol m-2 (leaf) s-1 MPa-1
  # K = K * par_plant$pl_sapw_area/par_plant$pl_ba*par_plant$st_basal_area*1e-4 #kg m-2 (ground) s-1 MPa-1
  # K = K * par_env$LAI #kg m-2 (leaf) s-1 MPa-1
  D = (par_env$vpd/par_env$patm)
  # D = par_env$vpd
  K/1.6/D * -integral_P(dpsi, psi_soil, par_plant$psi50, par_plant$b) #mol m-2 (leaf) s-1
}

get_std_photosythnesis_params = function(){ 
  ## Set P-model parameters
  kphio <- 0.05        # quantum yield efficiency
  # c_molmass <- 12.0107 # molar mass, g / mol
  
  ## Define environmental conditions
  tc <- 25             # temperature, deg C
  ppfd <- 400          # umol/m2/s
  # vpd  <- 1000         # Pa
  co2  <- 400          # ppm
  elv  <- 0            # m.a.s.l.
  fapar <- 0.7         # fraction
  
  p = rpmodel::calc_patm(elv)
  return (list(
    kmm = rpmodel::calc_kmm(tc, p),  # Why does this use std. atm pressure, and not p(z)?
    gammastar = rpmodel::calc_gammastar(tc, p),
    phi0 = kphio*rpmodel::calc_ftemp_kphio(tc),
    Iabs = ppfd*fapar,
    ca = co2*p*1e-6,  # Convert to partial pressure
    patm = p,
    delta = 0.00
  ))
}


fn_profit_phydro_sox_psi_soil <- function(par, e_crit, p_crit, par_cost, par_photosynth, 
                                 par_plant, par_env, do_optim = FALSE, opt_hypothesis){
  psi_soil = par[3]$psi_soil
  jmax = exp(par[1])$logjmax  # Jmax in umol/m2/s (logjmax is supplied by the optimizer)
  dpsi = par[2]$dpsi       # delta Psi in MPa
  psi_leaf = psi_soil-dpsi
  K = scale_conductivity_ks(par_plant$conductivity, par_env, par_plant, do_backtransform = FALSE)* par_env$LAI
  gs = calc_gs_test(dpsi, psi_soil, par_plant, par_env) * par_env$LAI # gs in mol/m2ground/s
  e  = 1.6*gs*(par_env$vpd/par_env$patm)         # E in mol/m2ground/s

  ## light-limited assimilation
  a_j   <- calc_assim_light_limited(gs, jmax, par_photosynth) # Aj in umol/m2ground/s
  a     = a_j$a
  ci    = a_j$ci
  vcmax = calc_vcmax_coordinated_numerical(a,ci, par_photosynth)
    ks         = K*(1/2)^(psi_soil/par_plant$psi50)^par_plant$b
    kl         = K*(1/2)^(psi_leaf/par_plant$psi50)^par_plant$b
    k_crit     = 0
    reduction_factor = (kl - k_crit)/(K - k_crit)
    cost = (par_cost$alpha * jmax)
    out <- a*reduction_factor - cost
  
  out <- tibble(cost = cost,
                risk = reduction_factor,
                out = out, #umolco2 m-2 s-1
                out_nocost = a*reduction_factor,
                vcmax = vcmax,
                jmax = jmax,
                a = a,
                E = e,
                gs = gs,
                psi_soil = psi_soil)
  return(out)
}

fn_profit_phydro_sox <- function(par, psi_soil, e_crit, p_crit, par_cost, par_photosynth, 
                                 par_plant, par_env, do_optim = FALSE, opt_hypothesis){
  
  jmax = exp(par[1])$logjmax  # Jmax in umol/m2/s (logjmax is supplied by the optimizer)
  dpsi = par[2]$dpsi       # delta Psi in MPa
  psi_leaf = psi_soil-dpsi
  K = scale_conductivity_ks(par_plant$conductivity, par_env, par_plant, do_backtransform = FALSE)* par_env$LAI
  gs = calc_gs_test(dpsi, psi_soil, par_plant, par_env) * par_env$LAI # gs in mol/m2ground/s
  e  = 1.6*gs*(par_env$vpd/par_env$patm)         # E in mol/m2ground/s

  ## light-limited assimilation
  a_j   <- calc_assim_light_limited(gs, jmax, par_photosynth) # Aj in umol/m2ground/s
  a     = a_j$a
  ci    = a_j$ci
  vcmax = calc_vcmax_coordinated_numerical(a,ci, par_photosynth)
    ks         = K*(1/2)^(psi_soil/par_plant$psi50)^par_plant$b
    kl         = K*(1/2)^(psi_leaf/par_plant$psi50)^par_plant$b
    k_crit     = 0
    reduction_factor = (kl - k_crit)/(ks - k_crit)
    cost = (par_cost$alpha * jmax)
    out <- a*reduction_factor - cost
  
  out <- tibble(cost = cost,
                risk = reduction_factor,
                out = out, #umolco2 m-2 s-1
                out_nocost = a*reduction_factor,
                vcmax = vcmax,
                jmax = jmax,
                a = a,
                E = e,
                gs = gs,
                psi_soil = psi_soil)
  return(out)
}


fn_profit_phydro_sox_test <- function(par, psi_soil, e_crit, p_crit, par_cost, 
                                      par_photosynth, par_plant, par_env, do_optim = FALSE, opt_hypothesis){
  
  jmax = exp(par[1])  # Jmax in umol/m2/s (logjmax is supplied by the optimizer)
  dpsi = par[2]#      # delta Psi in MPa
  psi_leaf = psi_soil-dpsi
  
  gs = calc_gs_test(dpsi, psi_soil, par_plant, par_env) * par_env$LAI  # gs in mol/m2ground/s
  e  = 1.6*gs*(par_env$vpd/par_env$patm)         # E in mol/m2ground/s
  
  ## light-limited assimilation
  a_j   <- calc_assim_light_limited(gs, jmax, par_photosynth) # Aj in umol/m2ground/s
  a     = a_j$a
  ci    = a_j$ci
  vcmax = calc_vcmax_coordinated_numerical(a,ci, par_photosynth)
  K = scale_conductivity_ks(par_plant$conductivity, par_env, par_plant, do_backtransform = FALSE)* par_env$LAI
    ks         = K*(1/2)^(psi_soil/par_plant$psi50)^par_plant$b
    kl         = K*(1/2)^(psi_leaf/par_plant$psi50)^par_plant$b
    k_crit     = 0
    reduction_factor = (kl - k_crit)/(ks - k_crit)
    cost = (par_cost$alpha * jmax)
    out <- a*reduction_factor - cost
    
  if (do_optim){
    return(-out)
  } else {
    return(out)
  }
}

optimise_stomata_phydro_test <- function(fn_profit, psi_soil, par_cost, e_crit, p_crit, par_photosynth, 
                                         par_plant, par_env, jmax_lim, return_all = FALSE, do_optim=TRUE, opt_hypothesis){
  if(is.null(jmax_lim)){jmax_lim = 7}
  
  out_optim <- optimr::optimr(
    par            = c(logjmax=-4, dpsi=(psi_soil-p_crit)/2),  
    lower          = c(-10, 0.001),
    upper          = c(jmax_lim,(psi_soil-p_crit)),
    fn             = fn_profit,
    psi_soil       = psi_soil,
    e_crit         = e_crit,
    p_crit         = p_crit,
    par_cost       = par_cost,
    par_photosynth = par_photosynth,
    par_plant      = par_plant,
    par_env        = par_env,
    do_optim       = do_optim,
    opt_hypothesis = opt_hypothesis,
    method         = "L-BFGS-B",
    control        = list(maxit = 500, maximize = TRUE, fnscale = 1e6)
  )
  
  out_optim$value <- -out_optim$value
  
  if (return_all){
    out_optim
  } else {
    return(out_optim$par)
  }
}

calc_phydro_sox_test <- function(tc, ppfd, vpd, co2, elv, LAI, fapar, kphio, psi_soil, par_plant, rdark, par_cost = NULL){
    patm = rpmodel::calc_patm(elv)
  par_photosynth <- list(
    kmm       = rpmodel::calc_kmm(tc, patm),
    gammastar = rpmodel::calc_gammastar(tc, patm),
    phi0      = kphio * rpmodel::calc_ftemp_kphio(tc),
    Iabs      = ppfd * fapar,
    ca        = co2 * patm * 1e-6,  # Convert to partial pressure
    patm      = patm,
    delta     = rdark
    # delta     = ftemp_inst_rd( tc )
  )
  par_env = list(
    viscosity_water = rpmodel::calc_viscosity_h2o(tc, patm),  # Needs to be imported from rpmodel.R
    density_water   = rpmodel::calc_density_h2o(tc, patm),  # Needs to be imported from rpmodel.R
    patm            = patm,
    tc              = tc,
    vpd             = vpd,
    LAI             = LAI
  )
  LAI        = par_env$LAI
  K          = scale_conductivity_ks(par_plant$conductivity, par_env, par_plant, do_backtransform = FALSE)*LAI #mol m-2 (ground) s-1 MPa-1
  p_crit = par_plant$psi50 * (log(1000)/log(2)) ^ ( 1/par_plant$b)
  e_crit = K * -integral_P_ecrit(psi_soil, par_plant$psi50, par_plant$b) #mol m-2 (ground) s-1
 
    # 2. if soil psi is lower than p_crit, set soil psi to 98% p_crit 
    low_swp <- FALSE
    if(psi_soil <= p_crit){
      psi_soil = p_crit*0.98
      low_swp  = TRUE
      print("WARNING: soil water potential is lower than critical plant water potential.")
    }
  
    # 3. Optimizer
  lj_dps = optimise_stomata_phydro_test(fn_profit_phydro_sox_test, 
                                     psi_soil = psi_soil, 
                                     e_crit = e_crit,
                                     p_crit= p_crit,
                                     par_cost  = par_cost, 
                                     par_photosynth = par_photosynth, 
                                     par_plant = par_plant, 
                                     par_env = par_env,
                                     jmax_lim = NULL,
                                     opt_hypothesis = "PM")

    jmax  = exp(lj_dps[1]) %>% unname()
    dpsi  = lj_dps[2] %>% unname()
    psi_l = psi_soil-dpsi
    gs    = calc_gs_test(dpsi, psi_soil, par_plant, par_env) * par_env$LAI # gs in mol m-2 (ground) s-1
    a_j   = calc_assim_light_limited(gs = gs, jmax = jmax, par_photosynth = par_photosynth)
    a     = a_j$a
    ci    = a_j$ci
    vcmax = calc_vcmax_coordinated_numerical(a, ci, par_photosynth)
    E     = 1.6 * gs * par_env$vpd/patm  # E in mol m-2 (ground) s-1
    #gs    = gs/patm*1e6 #transform to umol m-2(ground) s-1 Pa-1

    return(list(
      jmax         = jmax,
      dpsi         = dpsi,
      p_leaf       = psi_l,
      gs           = gs,
      E            = E,
      a            = a,
      ci           = ci,
      chi          = ci/par_photosynth$ca,
      vcmax        = vcmax,
      jmax_lim     = 0 
    ))
  }


par_cost = list(
  alpha = 0.1     # cost of jmax
)

p = rpmodel::calc_patm(0)

par_env = list(
  patm = p,
  viscosity_water = rpmodel::calc_viscosity_h2o(25, p),  # Needs to be imported from rpmodel.R
  density_water = rpmodel::calc_density_h2o(25, p),  # Needs to be imported from rpmodel.R
  tc = 25,
  vpd = 1000,
  LAI = 1.5
)

par_plant = list(
  # Ks0=1e-12,              # m2
  # v_huber=1e-4,           #
  height=10,              # m
  # conductivity_scalar=3,  # Scales (Ks0*v_huber/H)
  conductivity = 3e-17,
  psi50 = -3.46,             # Mpa
  d = -3.66,
  c = 6.55,
  b=6.55,                    # 
  rs = 0.1*1e-6,
  rr =2,
  dens_sapwood = 700
)

par_photosynth = get_std_photosythnesis_params()

psi_soil = -0.01

LAI        = par_env$LAI
K          = scale_conductivity_ks(par_plant$conductivity, par_env, par_plant, do_backtransform = FALSE)*LAI #mol m-2 (ground) s-1 MPa-1
p_crit = par_plant$psi50 * (log(1000)/log(2)) ^ ( 1/par_plant$b)
e_crit = K * -integral_P_ecrit(psi_soil, par_plant$psi50, par_plant$b) #mol m-2 (ground) s-1


jmax <- 3
pl <- seq(0.02,5,0.02)
par <- expand.grid(logjmax = jmax, dpsi = pl)

par %>% 
  split(seq(nrow(.))) %>% 
  purrr::map_df(function(x){
    fn_profit_phydro_sox(x,
                 psi_soil = psi_soil, 
                 e_crit = e_crit,
                 p_crit = p_crit,
                 par_cost = par_cost, 
                 par_photosynth = par_photosynth, 
                 par_plant = par_plant, 
                 par_env = par_env, 
                 do_optim = FALSE, 
                 opt_hypothesis = "LC")->res
    return(res)
  }) ->res

df_res <- res %>% cbind(par)
```

```{r,message = FALSE, warning=FALSE, echo = FALSE}

df_res %>% 
  ggplot()+
  geom_point(aes(dpsi,a), color = "#112CB9")+
  geom_point(aes(dpsi,risk), color = "#112CB9")+
  geom_point(aes(dpsi,out), color = "#FFB806")+
  geom_point(aes(dpsi,out_nocost), color = "red3")+
  geom_vline(aes(xintercept=df_res[which(df_res$out == df_res$out %>% max(na.rm = TRUE)),"dpsi"]), linetype = 2)+
  # geom_vline(aes(xintercept=df_res[which(df_res$out_nocost == df_res$out_nocost %>% max(na.rm = TRUE)),"dpsi"]), linetype = 2, color = "red")+
  ylab("OUT")+
  geom_text(x=3, y=-4, label="Example of Profit functions with VPD = 1 kPa, \n psi soil = -0.01 MPa and Jmax fixed",
            family = "arial", fontface = "italic")+
  theme_classic()+
  # ylim(-0.5,0.5)+
  NULL


```

Red line represents the profit optimization function of the original ProfitMax scheme. In yellow the proposed profit function. The upper blue line is the relative assimilation component and the lower is the normalized hydraulic penalization. The dashed vertical line represents the dpsi where the maximum profit is obtained.


The components of the profit maximization function can be rewritten as:
$$
A_j = g_\mathrm{s}  c_\mathrm{a} (1-\chi)
$$


$$
P(\psi) = \frac{1}{2} ^{(\frac{\psi}{\psi_{50}})^b}
$$

$$
k_\mathrm{\psi_s} = K_{max}\,P(\psi_s)= K_{max}\;(\frac{1}{2})^{(\frac{\psi_s}{\psi_{50}})^b}
$$


$$
k_\mathrm{\psi_l}= K_{max}\,P(\psi_l)=  K_{max}\;(\frac{1}{2})^{(\frac{\psi_l}{\psi_{50}})^b} = K_{max}\;(\frac{1}{2})^{(\frac{\psi_s - \Delta\psi }{\psi_{50}})^b}
$$

$k_\mathrm{\psi_{crit}}$ can be expressed as:
$$
k_\mathrm{\psi_{crit}} = K_{max}\;(\frac{1}{2})^{(\frac{\psi_{crit}}{\psi_{50}})^b}
$$

However we can assume that $k_\mathrm{\psi_{crit}} = 0$, which simplifies the optimization function.

Which gives us the next expression that can be solved similarly as in the P Hydro analytical approximation, where each term is a function of the two independent variables $\chi$ and $\Delta \psi$.
$$
F = g_\mathrm{s}  c_\mathrm{a} (1-\chi) (\frac{(\frac{1}{2})^{(\frac{\psi_s-\Delta\psi}{\psi_{50}})^b}}{(\frac{1}{2})^{(\frac{\psi_s}{\psi_{50}})^b}}) - \alpha J_\mathrm{max}
$$


Solved by $\chi$
$$
\frac{\partial F}{\partial \chi} =  - g_s\,c_a\,((\frac{1}{2})^{(\frac{\psi_s-\Delta\psi}{\psi_{50}})^b-(\frac{\psi_s}{\psi_{50}})^b})-\alpha\frac{\partial J_\mathrm{max}}{\partial A_{Jm}} \frac{\partial A_{Jm}}{\partial \chi} = 0
$$

Solved by $\Delta\psi$
$$
\frac{\partial F}{\partial \Delta\psi} = - \frac{1}{\psi_{50}}(\alpha\,\psi_{50}\,\frac{\partial J_\mathrm{max}}{\partial A_{Jm}} \frac{\partial A_{Jm}}{\partial \Delta\psi} - c_a\,(\frac{1}{2})^{(\frac{\psi_s-\Delta\psi}{\psi_{50}})^b-(\frac{\psi_s}{\psi_{50}})^b}(g_s\,(ln(2)\,\chi-ln(2))\,b\,(\frac{\psi_s-\Delta\psi}{\psi_{50}})^{b-1}-\psi_{50}(\chi-1)\frac{\partial g_s}{\partial \Delta\psi}))=0
$$


Here I show surfaces obtained from the optimization function numerically at four different $\psi_{s}$, a) -0.01, b) -1, c) -2 and d) -3 MPa (VPD = 1kPa). 
```{r,message = FALSE, warning=FALSE, echo = FALSE}

par_plant = list(
    conductivity = 1e-16,
    psi50 = -1.46,
    b=1.4
  )

par_cost = list(
  alpha = 0.1     # cost of jmax
)
jmax <- log(c(10,30,50))
# jmax <- 4
pl <- seq(0.02,2,0.005)
par <- expand.grid(logjmax = jmax, dpsi = pl)

psi_soil = 0
e_crit = K * -integral_P_ecrit(psi_soil, par_plant$psi50, par_plant$b) #mol m-2 (ground) s-1
par %>% 
  split(seq(nrow(.))) %>% 
  purrr::map_df(function(x){
    fn_profit_phydro_sox(x,
                 psi_soil = psi_soil,
                 e_crit = e_crit,
                 par_cost = par_cost, 
                 par_photosynth = par_photosynth, 
                 par_plant = par_plant, 
                 par_env = par_env, 
                 do_optim = FALSE, 
                 opt_hypothesis = "LC")->res
    return(res)
  }) ->res

df_res1 <- res %>% cbind(par)%>% mutate(jmax = as.factor(round(jmax,1)))

ggplot()+
  geom_line(data = df_res1, aes(dpsi,a*risk, color = jmax, group = jmax), linetype =2, show.legend = FALSE)+
  geom_line(data = df_res1,aes( dpsi,cost, color = jmax, group = jmax), linetype =4)+
  geom_line(data = df_res1, aes( dpsi,out, color = jmax, group = jmax), linetype =1)+
  geom_vline(aes(xintercept=df_res1[which(df_res1$out == df_res1$out %>% max(na.rm = TRUE)),"dpsi"]), linetype = 3, color= "#009E73")+
  ylab("OUT")+
  # geom_text(x=2, y=-10, label="Example of the Profit surface \n with VPD = 1 kPa, psi soil = -0.01 MPa",
  #           family = "arial", fontface = "italic")+
  theme_classic()+
  scale_color_manual(values =  c("#56B4E9", "#009E73", "#F0E442"))+#colorRampPalette(c("red", "gray50"))(3)) +
  ylim(-0.1,5.5)+
  xlab(expression("|"*psi[l]*"| (MPa)"))+
  theme(plot.margin = unit(c(0,0.1,-4,0.1), "cm"))+
  NULL -> f1


ggplot()+
  geom_line(data = df_res1, aes(gs,a*risk, color = jmax, group = jmax), linetype =2, show.legend = FALSE)+
  geom_line(data = df_res1,aes(gs,cost, color = jmax, group = jmax), linetype =4)+
  geom_line(data = df_res1, aes(gs,out, color = jmax, group = jmax), linetype =1)+
  geom_vline(aes(xintercept=df_res1[which(df_res1$out == df_res1$out %>% max(na.rm = TRUE)),"gs"]), linetype = 3, color= "#009E73")+
  ylab("OUT")+
  # geom_text(aes(x=0.05, y=1, label=as.character(expression("|"*psi[s]*"| = 0 MPa"))), parse = TRUE, size = 3)+
  theme_classic()+
  scale_color_manual(values =  c("#56B4E9", "#009E73", "#F0E442"))+#colorRampPalette(c("red", "gray50"))(3)) +
  ylim(-0.1,5.5)+
  xlim(0,0.15)+
  xlab(expression(atop("g"[s]~"(mol m"^-2~"s"^-1*")")))+
  theme(plot.margin = unit(c(0,0.1,-4,0.1), "cm"))+
  NULL -> f2

jmax <- log(c(5,20,35))
# jmax <- 4
pl <- seq(0.02,2,0.005)
par <- expand.grid(logjmax = jmax, dpsi = pl)

psi_soil = -3
e_crit = K * -integral_P_ecrit(psi_soil, par_plant$psi50, par_plant$b) #mol m-2 (ground) s-1
par %>% 
  split(seq(nrow(.))) %>% 
  purrr::map_df(function(x){
    fn_profit_phydro_sox(x,
                 psi_soil = psi_soil,
                 e_crit = e_crit,
                 par_cost = par_cost, 
                 par_photosynth = par_photosynth, 
                 par_plant = par_plant, 
                 par_env = par_env, 
                 do_optim = FALSE, 
                 opt_hypothesis = "LC")->res
    return(res)
  }) ->res

df_res2 <- res %>% cbind(par) %>% mutate(jmax = as.factor(round(jmax,1)))

ggplot()+
  geom_line(data = df_res2, aes(-psi_soil+dpsi,a*risk, color = jmax, group = jmax), linetype =2, show.legend = FALSE)+
  geom_line(data = df_res2,aes( -psi_soil+dpsi,cost, color = jmax, group = jmax), linetype =4)+
  geom_line(data = df_res2, aes( -psi_soil+dpsi,out, color = jmax, group = jmax), linetype =1)+
  geom_vline(aes(xintercept=df_res2[which(df_res2$out == df_res2$out %>% max(na.rm = TRUE)),"dpsi"]-psi_soil), linetype = 3, color= "#009E73")+
  ylab("OUT")+
  # geom_text(x=2, y=-10, label="Example of the Profit surface \n with VPD = 1 kPa, psi soil = -0.01 MPa",
  #           family = "arial", fontface = "italic")+
  theme_classic()+
  scale_color_manual(values = c("#56B4E9", "#009E73", "#F0E442"))+#colorRampPalette(c("red", "gray50"))(3)) +
  ylim(-0.1,0.5)+
  xlim(-psi_soil,-psi_soil+2)+
  xlab(expression("|"*psi[l]*"| (MPa)"))+  
  theme(plot.margin = unit(c(0,0.1,-4,0.1), "cm"))+
  NULL -> f3

ggplot()+
  geom_line(data = df_res2, aes(gs,a*risk, color = jmax, group = jmax), linetype =2, show.legend = FALSE)+
  geom_line(data = df_res2,aes(gs,cost, color = jmax, group = jmax), linetype =4)+
  geom_line(data = df_res2, aes(gs,out, color = jmax, group = jmax), linetype =1)+
  geom_vline(aes(xintercept=df_res2[which(df_res2$out == df_res2$out %>% max(na.rm = TRUE)),"gs"]), linetype = 3, color= "#009E73")+
  ylab("OUT")+
  # geom_text(aes(x=0.05, y=1, label=as.character(expression("|"*psi[s]*"| = 4 MPa"))), parse = TRUE, size = 3)+
  theme_classic()+
  scale_color_manual(values =  c("#56B4E9", "#009E73", "#F0E442"))+#colorRampPalette(c("red", "gray50"))(3)) +
  ylim(-0.1,0.5)+
  xlim(0,0.15)+
  xlab(expression(atop("g"[s]~"(mol m"^-2~"s"^-1*")")))+
  theme(plot.margin = unit(c(0,0.1,-4,0.1), "cm"))+
  NULL -> f4

# 
# cowplot::plot_grid(f1,f2,f3,f4, labels = "auto",
#           ncol = 2, nrow = 2)
plot1 <- ggarrange(f1,f2, labels = c("A","B"), common.legend = TRUE, legend = "top",
                                    ncol = 2, nrow = 1, align="h",font.label = list(size = 10 ))
# plot1 <- annotate_figure(plot1,top =text_grob(expression("|"*psi[s]*"| = 0 MPa", size = 5)))
plot2 <- ggarrange(f3,f4, labels = c("C","D"),common.legend = TRUE, legend = "top",
                                    ncol = 2, nrow = 1, align="h" ,font.label = list(size = 10))
# plot2 <- annotate_figure(plot2,top =text_grob(expression("|"*psi[s]*"| = 3 MPa"),size = 10))
ggarrange(plot1,plot2,ncol = 1, nrow = 2, align="hv")


```


```{r,message = FALSE, warning=FALSE, echo = FALSE}

par_plant = list(
    conductivity = 1e-16,
    psi50 = -1.46,
    b=1.2
  )
jmax <- seq(-10,3.5,0.5)
pl <- seq(0.01,1.5,0.01)
psi_soil <- seq(0,-8,-1)
par <- expand.grid(logjmax = jmax, dpsi = pl, psi_soil = psi_soil)

# e_crit = K * -integral_P_ecrit(psi_soil, par_plant$psi50, par_plant$b) #mol m-2 (ground) s-1
par %>% 
  split(seq(nrow(.))) %>% 
  purrr::map_df(function(x){
    fn_profit_phydro_sox_psi_soil(x,
                 par_cost = par_cost, 
                 par_photosynth = par_photosynth, 
                 par_plant = par_plant, 
                 par_env = par_env, 
                 do_optim = FALSE, 
                 opt_hypothesis = "LC")->res
    return(res)
  }) ->res

df_res5 <- res %>% cbind(dpsi = par[,2]) %>% 
  mutate(out = exp(out) %>% as.numeric(),
         psi_soil = factor(psi_soil, 
                              levels = rev(c("-8","-7","-6","-5","-4","-3","-2","-1","0")),
                              labels = rev(c("-8 MPa","-7 MPa","-6 MPa","-5 MPa",
                              "-4 MPa","-3 MPa","-2 MPa","-1 MPa","0 MPa"))))

max_out <- df_res5 %>% 
  group_by(psi_soil) %>% 
  filter(out == max(out, na.rm = TRUE)) 


df_res5 %>% 
  ggplot()+
  geom_contour_filled(aes(x=dpsi, y = jmax, z = out))+#, show.legend = FALSE)+
  geom_point(data = max_out, aes(x=dpsi,y=jmax),shape=3)+
  facet_wrap(~ psi_soil)+
  theme_bw()+
  theme(strip.background = element_rect(fill="transparent"))+
  ylab(expression(atop(J["max"],"("*mu*"mol/m"^2*"/s)")))+
  xlab(expression(atop(Delta*psi,"(MPa)")))+
  viridis::scale_fill_viridis(discrete=TRUE)

```


```{r echo=F}
plot_all = function(df_w_vol, varname, ref=NULL){

    my_theme = function(){
      theme_classic()+
      theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14),
        plot.tag.position = "topleft")
  }

  p1 <- df_w_vol %>%
  ggplot() +
    my_theme()+
  geom_line(aes(x = var, y = out_hydraulics_vcmax), col="green3", size=1) +
  # geom_line(aes(x = var, y = out_analytical_vcmax ), col="grey", size=1) +
  expand_limits(y=0)+
    xlab(varname)+
    ylab(expression(atop(V["cmax"],"("*mu*"mol/m"^2*"/s)")))

p2 <- df_w_vol %>%
  ggplot() +
    my_theme()+
  geom_line(aes(x = var, y = out_hydraulics_dpsi), col="blue", size=1)+
  expand_limits(y=0)+
    xlab(varname)+
  ylab(expression(atop(Delta*psi,"(MPa)")))

p3 <- df_w_vol %>%
  ggplot() +
  my_theme()+
  geom_line(aes(x = var, y = out_hydraulics_gs), col="cyan2", size=1)+
  # geom_line(aes(x = var, y = out_analytical_gs), col="grey", size=1)+
  expand_limits(y=0)+
    xlab(varname)+
  ylab(expression(atop(g[s],"(mol/m"^2*"/s)")))

p4 <- df_w_vol %>%
  ggplot() +
    my_theme()+
  geom_line(aes(x = var, y = out_hydraulics_chi), col="magenta", size=1)+
  # geom_line(aes(x = var, y = out_analytical_chi), col="grey", size=1)+
  # geom_line(aes(x = var, y = out_hydraulics_chi_jmax_lim), col="violet", size=0.5)+
  expand_limits(y=0)+
    xlab(varname)+
  ylab(expression(chi))

p5 <- df_w_vol %>%
  ggplot() +
    my_theme()+
  # geom_line(aes(x = var, y = out_analytical_jmax), col="grey", size=1) +
  geom_line(aes(x = var, y = out_hydraulics_jmax), col="goldenrod1", size=1) +
  expand_limits(y=0)+
  xlab(varname)+
  ylab(expression(atop(J["max"],"("*mu*"mol/m"^2*"/s)")))

p6 <- df_w_vol %>%
  ggplot() +
    my_theme()+
  geom_line(aes(x = var, y = out_hydraulics_a), col="green4", size=1) +
  # geom_line(aes(x = var, y = out_analytical_gpp), col="grey",size=1) +
  expand_limits(y=0)+
    xlab(varname)+
  ylab(expression(atop(A,"("*mu*"mol/m"^2*"/s)")))

if (!is.null(ref)){
  p1 <- p1 +
    geom_point(data=ref, aes(x = var, y = out_hydraulics_vcmax), col="green4", size=1) 
  p2 <- p2 +
    geom_point(data=ref, aes(x = var, y = out_hydraulics_dpsi), col="blue4", size=1) 
  p3 <- p3 +
    geom_point(data=ref, aes(x = var, y = out_hydraulics_gs), col="cyan3", size=1) 
  p4 <- p4 +
    geom_point(data=ref, aes(x = var, y = out_hydraulics_chi), col="magenta4", size=1) 
  p5 <- p5 +
    geom_point(data=ref, aes(x = var, y = out_hydraulics_jmax), col="orange4", size=1) 
  p6 <- p6 +
    geom_point(data=ref, aes(x = var, y = out_hydraulics_a), col="darkgreen", size=1) + expand_limits(y=0)  
}

 list(p6, p1, p5, p4,
      p3, p2)

}

```

Here I show the simulations for the soil potential gradient. The plant have a $\psi_{50}$ = -3.46 a slope parameter of 6.55 and a $K$ of 3e-17
```{r,echo=FALSE}

# phydro_sox_bf <- function(x){
#     psi_soil <- x
#     jmax <- seq(1,5,0.2)
#     pl <- seq(0.02,3.4,0.02)
#     par <- expand.grid(logjmax = jmax, dpsi = pl)
#     e_crit = K * -integral_P_ecrit(psi_soil, par_plant$psi50, par_plant$b) #mol m-2 (ground) s-1
#     par %>% 
#     split(seq(nrow(.))) %>% 
#     purrr::map_df(function(y){
#     fn_profit_phydro_sox(y,
#                  psi_soil = psi_soil, 
#                  e_crit = e_crit,
#                  par_cost = par_cost, 
#                  par_photosynth = par_photosynth, 
#                  par_plant = par_plant, 
#                  par_env = par_env, 
#                  do_optim = FALSE, 
#                  opt_hypothesis = "LC")->res
#     return(res)
#   }) ->res
#     res <- res %>% cbind(par)
# return(as.list(res[which(res$out == res$out %>% max(na.rm = TRUE)),]))
# }

# dat_soilm_numerical = tibble(var=seq(-5,0,length.out=10)) %>% 
#   mutate(out_hydraulics = purrr::map(var, ~phydro_sox_bf(.)) ) %>%
#   unnest_wider(out_hydraulics, names_sep = "_")
dat_soilm_numerical = tibble(var=seq(-6,0,length.out=20)) %>% 
  mutate(out_hydraulics = purrr::map(var, ~calc_phydro_sox_test(tc = 25, ppfd = 400, vpd = 1000, co2 = 400, elv = 0,LAI = 1.5, fapar = 0.7, kphio = 0.087, psi_soil = .,  par_plant = par_plant, rdark = 0.02, par_cost = list(alpha=0.1)))) %>%
  unnest_wider(out_hydraulics, names_sep = "_")


l1= dat_soilm_numerical %>% 
  plot_all(expression(psi["s"]~"(MPa)"), ref = dat_soilm_numerical)

cowplot::plot_grid(plotlist = l1, labels="", label_size = 16, label_colour = "grey50", label_x = 0.3, hjust = 0, align = "hv", rel_widths = 1, nrow=3, byrow=T)
```

And here the simulations for VPD. Lines are simulations with $\psi_s$ equal to -1 MPa and dots -3 MPa.
```{r,echo=FALSE}

dat_vpd_numerical = tibble(var=seq(100,3000,length.out=20)) %>% 
  mutate(out_hydraulics = purrr::map(var, ~calc_phydro_sox_test(tc = 25, ppfd = 400, vpd = ., co2 = 400, elv = 0,LAI = 1.5, fapar = 0.7, kphio = 0.087, psi_soil = -1,  par_plant = par_plant, rdark = 0.02, par_cost = list(alpha=0.1)))) %>%
  unnest_wider(out_hydraulics, names_sep = "_")

dat_vpd2_numerical = tibble(var=seq(100,3000,length.out=20)) %>% 
  mutate(out_hydraulics = purrr::map(var, ~calc_phydro_sox_test(tc = 25, ppfd = 400, vpd = ., co2 = 400, elv = 0,LAI = 1.5, fapar = 0.7, kphio = 0.087, psi_soil = -3,  par_plant = par_plant, rdark = 0.02, par_cost = list(alpha=0.1)))) %>%
  unnest_wider(out_hydraulics, names_sep = "_")


l2= dat_vpd_numerical %>% mutate(var = var/1000) %>% 
  plot_all(expression(VPD~"(kPa)"), ref = dat_vpd2_numerical%>% mutate(var = var/1000))

cowplot::plot_grid(plotlist = l2, labels="", label_size = 16, label_colour = "grey50", label_x = 0.3, hjust = 0, align = "hv", rel_widths = 1, nrow=3, byrow=T)


```


